%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
  {\Huge \scshape Rahul I Basaragi} \\[4pt]
  \begin{minipage}[t]{0.3\textwidth}
    \raggedright
    \faPhone~ +91-861-848-5610 \\
    \faEnvelope~ \href{mailto:rahulib7172@gmail.com}{rahulib7172@gmail.com}
  \end{minipage}
  \begin{minipage}[t]{0.35\textwidth}
    \centering
    \faGlobe~ \href{https://rahulibasaragi.tech}{Portfolio} \\
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \raggedleft
    \faLinkedin~ \href{https://www.linkedin.com/in/rahul-i-basaragi-05886829b/}{LinkedIn} \\
    \faGithub~ \href{https://github.com/RahulIB5}{GitHub}
  \end{minipage}
\end{center}




%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar College of Engineering} {2023 -- 2027}
      {Bachelor of Engineering in Computer Science and Engineering } {\textbf{CGPA: 9.15}}
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, C++, HTML, CSS} \\
     \textbf{Technologies/Frameworks}{: Next.JS, React.JS, Three.JS, Node.JS, Express.JS,  ejs, Bootstrap, Tailwind CSS} \\
     \textbf{Database Management}{: MongoDB, PostgreSQL, Firebase, Supabase, SQLite} \\
     \textbf{UI/UX and Design}{: Figma (Wireframing and Prototyping), Canva (Presentation and Graphics)} \\
     \textbf{Other Tools}{: VS Code, Git, GitHub, PyCharm, Vercel, Render} \\
     \textbf{Soft Skills}{: Presentation Skills, Communication Skills, Team Collaboration } \\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Whisper - MERN Stack Chat Application} $|$ \emph{MongoDB, Express, React, Node.js, Socket.io, TailwindCSS} $|$ \href{https://github.com/RahulIB5/Whisper}{\textbf{Github}}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-featured real-time chat application using the \textbf{MERN} stack with \textbf{Socket.io} for instant messaging.}
            \resumeItem{Implemented \textbf{JWT} authentication and authorization with \textbf{Zustand} for global state management.}
            \resumeItem{Integrated features including \textbf{real-time messaging}, online status indicators, image sharing, custom profile pictures, and 32 UI themes.}
            \resumeItem{Designed responsive UI with \textbf{TailwindCSS} and \textbf{Daisy UI}, while implementing comprehensive error handling on both server and client sides.}
          \resumeItemListEnd
          \vspace{-13pt}

          \resumeProjectHeading
  {\textbf{Aurora - Blogging Platform} $|$ \emph{Next.js, TypeScript, Prisma, PostgreSQL} $|$ \href{https://github.com/RahulIB5/zblog}{\textbf{GitHub}}}{}
  \resumeItemListStart
    \resumeItem{Developed a modern blogging platform with features like user authentication (Sign up, Sign in, Sign out) using \textbf{Clerk}.}
    \resumeItem{Implemented \textbf{CRUD} functionality for blog posts with a rich text editor (React Quill), along with \textbf{like}, \textbf{comment}, and \textbf{keyword search} features.}
    \resumeItem{Designed a responsive UI using Tailwind CSS and shadcn/ui, supporting a personalized user dashboard.}
    \resumeItem{Utilized \textbf{Next.js 15} (App Router) with server actions, dynamic routing for SEO, and type-safe development with TypeScript, \textbf{Prisma}, and \textbf{Zod}.}
  \resumeItemListEnd
  \vspace{-13pt}

        \resumeProjectHeading
          {\textbf{AI Recipe Generator} $|$ \emph{React.js, Mistral AI, Hugging Face API} $|$ \href{https://github.com/RahulIB5/Recipe-Gen}{\textbf{Github}}}{}
          \resumeItemListStart
            \resumeItem{RecipeGen is a \textbf{React-based AI-powered} recipe generator that creates personalized recipes based on user-inputted ingredients or preferences.}
            \resumeItem{It utilizes \textbf{Mistral AI} and the \textbf{Hugging Face API} to generate unique recipes instantly.}
            \resumeItem{The application is built with React.js providing a simple and efficient user experience.}
          \resumeItemListEnd
\vspace{-15pt}

\resumeProjectHeading
  {\textbf{MERN Agent Task Distribution System} $|$ \emph{MERN Stack, Tailwind CSS, ShadCN UI, Vite, TypeScript} $|$ \href{https://github.com/RahulIB5/Agent-Manager}{\textbf{GitHub}}}{}
  \resumeItemListStart
    \resumeItem{Built a full-stack web app to manage agents and distribute tasks from uploaded \textbf{CSV/XLSX} files equally among them.}
    \resumeItem{Implemented \textbf{JWT-based authentication}, admin dashboard, and protected routes using Express.js and MongoDB.}
    \resumeItem{Enabled \textbf{CSV parsing}, agent-wise task allocation logic, and persistent data storage.}
    \resumeItem{Designed a responsive UI with \textbf{TailwindCSS} and \textbf{ShadCN UI}, optimized with Vite + TypeScript for performance.}
  \resumeItemListEnd
\vspace{-13pt}

      
     \resumeProjectHeading
        {\textbf{Tenzies Game} $|$ \emph{React.js, CSS, JavaScript} $|$ \href{https://github.com/RahulIB5/Tenzieeeesss}{\textbf{Github}}}{}
        \resumeItemListStart
          \resumeItem{Developed a fun and fast-paced dice game in which players roll ten dice, with the aim of matching all to the same number.}
          \resumeItem{Implemented \textbf{React state management} to track dice values, roll counts, and game timer functionality.}
          \resumeItem{Utilized \textbf{React hooks} \textbf{(useState, useEffect)} to manage component lifecycle and side effects.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

        \vspace{-13pt}
      

    

%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubItem{\textbf{\href{https://www.instagram.com/bytexync/}{ByteXync} - PR Team Member} \hfill \textit{Sept 2024 -- Present}}
            \resumeItemListStart
                \resumeItem{Managed social media content and marketing initiatives to increase campus engagement with tech-focused events.}
                \resumeItem{Helped coordinate outreach efforts to build connections with industry professionals and \textbf{sponsors}.}
            \resumeItemListEnd
                
        \resumeSubItem{\textbf{\href{https://www.instagram.com/oscodedsce/}{OSCodeDSCE} - Marketing Team Member} \hfill \textit{Dec 2024 -- Present}}
            \resumeItemListStart
                \resumeItem{Created engaging content for social media platforms to increase community participation.}
                \resumeItem{Assisted in organizing coding sessions and hackathons to foster collaboration among student developers.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

    


\end{document}
